### 2020-06-28 introduction.tex
abs+parial intro

% introduce LPL asynchronous duty cycle media access
As already we are aware, smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day. As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing". 
Assuming that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes. And studies show that a great portion of these attacks are casual and opportunistic without technical equipment~\cite{eiband2017understanding}, say a mere stranger can hardly do any harm reading a fragment of the correspondence or acquiring the password without knowing the account for critical apps like Alipay, which seldom appears on screen in common usages. 
% It is however the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can do the most harm. The attacker can even be our closest friends or family members, as there are various cases in China where a child obtains Alipay password of their parents and is unaware that electronic payments consists of 'real' money, resulting in spending them lavishly in their games. Besides, specially designed equipment are not a necessity for the shoulder surfing attack.

The privacy threat however has been exacerbated with smartphones improved significantly these years. Given the commercial smartphone, the attacker can not only reduce suspicion by acquiring sensitive information from a long distance, but also record the information for propagating, rendering greater damage to the victim. For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}.Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones. Hardware improvements in memory also allows the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second. And more images means more recorded information of the victim. To gain vital data stealthily from even further away, the processing technique of multi-frame super resolution (SR) algorithms can be employed by the attacker, delivering a more threatening shoulder surfing model.

@@

To mitigate this threat, massive efforts have been made, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}. All of these methods however require additional cost and/or effort \cite{Chun2019Keep} and are not widely deployed yet on the critical privacy stages (e.g., password entry) of most everyday apps. And none of existing work can deal with the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios. Given that the leakage of a password and the disclosure of correspondence of public figures can cause great damage to the victim, we believe that it's imminent to recall attention on this new privacy threat and propose the corresponding standard of screen protection based on modern circumstances.

\cl{The challenge part can be revised to make it more precise. And it can be described with the new figure.}
\vspace{1mm}
\noindent
\textbf{challenges.} Creating a high-resolution shoulder surfing attack model running on commercial smartphones in real time, however, is not trivial. And we achieve \textsf{SRPeek} by overcoming three key challenges.

\begin{itemize}[leftmargin=*]
  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness, as our photos are taken at extreme range, taken secretly and hurriedly without much room for focusing, while straining the magnification of the smartphone lenses. Unlike most SR applications and datasets working with ‘normally’ captured photos, the images we face exhibit lower concentrations of information and more artifacts, and needs more ‘reconstruction’ than ‘interpolation’.
  \item \textbf{Processing with multi-frames.} While exploring this privacy threat, we need a multi-frame SR algorithm on a smartphone to monitor the target phone in real time. However, we discover that there is no existing SR algorithm suitable for this scenario. On one hand, images captured by hand are blurred while most methods rely on a handful of clearer images (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}. Specifically, we have to extract the information from large quantities of extremely blurred photos, as smartphones can capture 100 snapshots in a few seconds in burst mode, and these photos are taken from extreme distances. On the other hand, the difference between videos and multiple snapshots rules out the video super resolution algorithms, which cannot be adapted to larger numbers of input images. The reason has two folds. First, either increased input leads to increases in model complexity, making it unsuitable for mobile deployment. Second, they lack an emphasis on the process of horizontal comparison(??) by relying heavily on the information extracted from each single image, resulting in an inefficient merge of information from multiple frames.
  \item \textbf{Compatibility with various characters.} Another difficulty unique to our task is the subject—mainly, Chinese characters. Composed of multiple strokes, these characters are distributed discretely in image space, not known to other entities, e.g. faces and natural objects. In some cases, messing up a stroke will not impact its readability, and in other cases shortening or lengthening a stroke even slightly will lead to a different character, leading to misunderstandings. And unlike most SR applications working on similarity (between their output and the ‘ground truth’), our goal is readability, and the network architecture and training process must be engineered accordingly.
\end{itemize}

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/zeros.png}
    \caption{Photos of number ‘0’ on a screen at a distance of 1.5m, taken in quick succession from a still smartphone camera. All exhibit different blurriness and no consistency between neighboring frames.\cl{Figure should be replaced.}}
	\label{fig-zeros}
\end{figure}

\cl{The following part can correspond to challenges above. Remember to be precise and illustrative.}
In this paper, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing for commercial smartphones. To fully explore this privacy threat with the multi-frame super resolution, we first design a deep learning architecture using convolutional neural network (CNN). With the specially designed network as core, we deliver a holistic system for shoulder surfing on a smartphone. Then it processes them with our neural network to generate a high-resolution image and repeats the process for constant monitoring. As the information of interest is mostly in the form of text (e.g., passwords or e-mails), our network is trained and evaluated on the task of reconstructing text, specifically, Chinese characters, English letters, and numbers, but we believe that this network architecture can function in all scenarios. Our system can also be used as a preprocessor for text-recognition applications when multiple images are available, such as real-time translation apps on a smartphone or text-recognition on self-driving cars.

To deal with massive frames of blurred images with limited computational resources on smartphones, we design an unique merging layer and place it between convolutional layers in the SR pipeline. Thus information can be extracted first from input images independently and then merged together, serving as a reference for the following convolutions.

As mentioned above, reconstructing images with high degrees of blurriness requires a unique approach. Most works on multi-frame SR function on video clips \cite{lucas2019generative} or multiple snapshots \cite{wronski2019handheld}, however, our application is subtly different from the two. Our dilemma is as follows: on one hand, each one of the photos we are to process is blurred with a randomly different PSF kernel, which, because of the extreme blurriness, cannot be approximated as a constant, isotropic gaussian kernel, and thus lacking consistency between neighboring frames, meaning that they cannot be processed as a video clip(see Figure~\ref{fig-zeros} ); on the other hand, because of the low concentration of information, the blurred photos are similar to pieces of a jigsaw puzzle, each containing only fractions of information, and the only chance of recovering the ground truth is by comparing each photo against others. If processed by common procedures enhancing the resolution of a series of snapshots—processing each one separately and merging them afterwards, few useful information can be extracted from each one of the images, and merging them will not produce satisfactory results.

Considering the unique challenges of our application, we believe that if these images are processed iteratively, alternating between the following two processes, our network will be able to solve this ‘jigsaw puzzle’:

\begin{enumerate}
  \item Every single image of the input collection will be processed solely (by several layers of CNN), with access of the output of step (2) of the last iteration;
  \item The processed results will be merged (with weighted averaging methods) and distributed to each photo for the next iteration.
\end{enumerate}

This architecture is beneficial to our task. On one hand, the deep learning part is assigned to each single image, reducing computational complexity and parameter growth, while receiving a global view of all the images, renewed at each layer, thanks to the merging process; on the other hand, information can be shared horizontally with weighted averaging methods, meaning no consideration of sequential order and no reliance of consistency between neighboring frames. Thus, this architecture solves the dilemma mentioned above, and proves perfectly functional in our application.

>>>>

% introduce LPL asynchronous duty cycle media access
As already we are aware, smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day. As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing". 
Given that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes. And studies show that a great portion of these attacks are casual and opportunistic without technical equipment~\cite{eiband2017understanding}, say a mere stranger can hardly do any harm reading a fragment of the correspondence or acquiring the password without knowing the account for critical apps like Alipay, which seldom appears on screen in common usages. 
% It is however the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can do the most harm. The attacker can even be our closest friends or family members, as there are various cases in China where a child obtains Alipay password of their parents and is unaware that electronic payments consists of 'real' money, resulting in spending them lavishly in their games. Besides, specially designed equipment are not a necessity for the shoulder surfing attack.

The privacy threat however has been exacerbated with the rapidly developed mobile camera module these years. Given the commercial smartphone, the attacker cannot acquire sensitive information from a long distance to reduce suspicion, but also recognize the information accurately for propagating, making existing defense work ineffective. For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}. Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones. Hardware improvements in memory also allows the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second. And more images mean more recorded information of the victim. To gain vital data stealthily and accurately from even further away, the processing technique of multi-frame super resolution (SR) algorithms can be further employed by the attacker, delivering a long-range shoulder surfing threat model.

@@

To mitigate this threat, massive efforts have been made, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}. All of these methods however require additional deployment cost \cite{Chun2019Keep} and cannot be widely deployed for critical privacy stages (e.g., password entry) of most scenarios. Furthermore, none of existing works can deal with the presence of developed smartphone cameras and SR algorithms in shoulder surfing scenarios. Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it's imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.

In this paper, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm. Deployed on commercial smartphones, it can take multiple snapshots of the target screen continuously and stealthily from a long range, illustrated in Figure~\ref{illustration_of_system}. Benefited from our multi-frame SR neural network, those blurred images can be then aligned, cropped, and processed, delivering a holistic threat model for acquisition of high-resolution contents of the victim.

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/intro.png}
    \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm. \cl{supplement elements for long range, blurred input and the recognized results.}}
	\label{illustration_of_system}
\end{figure}

\vspace{1mm}
\noindent
\textbf{Challenges.} Creating a high-resolution shoulder surfing threat model, however, is not trivial, especially for commercial smartphones in real time. And we achieve \textsf{SRPeek} by overcoming four key challenges.

% \begin{figure}
% 	\centering
% 	\includegraphics[width=0.48\textwidth]{pic/zeros.png}
%     \caption{Photos of number ‘0’ on a screen at a distance of 1.5m, taken in quick succession from a still smartphone camera. All exhibit different blurriness and no consistency between neighboring frames.\cl{Figure should be replaced.}}
% 	\label{illustration_of_system}
% \end{figure}

\begin{itemize}[leftmargin=*]
  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without much room for focusing. It can be further exacerbated by straining the magnification of the smartphone lenses. Unlike most SR applications and datasets working with ``normally" captured photos (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, images we face exhibit lower concentrations of information and more artifacts, and needs reliable ``reconstruction" than ``interpolation"". Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character. 
  % In deep learning based methods, a deep network often leads to gradual divergence from the truth as the data is propagated deeper through the network pipeline, resulting in 'fake' high-res images, especially when the subjects are the discrete strokes of characters, instead of details and texture of everyday objects. As a matter of fact, most works on multi-frame SR function on video clips \cite{lucas2019generative} or multiple snapshots \cite{wronski2019handheld}, however, our application is subtly different from the two. 
  On one hand, each photo is blurred with a randomly different PSF kernel, which, because of the extreme blurriness, cannot be approximated as a constant, isotropic gaussian kernel. Thus they cannot be processed as a video clip due to the lacking consistency between neighboring frames\cl{citation?}, shown in Figure~\ref{illustration_of_system}; on the other hand, because of the low concentration of information, blurred photos are similar to pieces of a jigsaw puzzle, each containing only fractions of information.
  % and the only chance of recovering the ground truth is to compare each photo against others. 
  Few useful information can be extracted separately and merged directly to produce satisfactory results if processed by common procedures to enhance the resolution of a series of snapshots\cl{citation?}. 
  \item \textbf{Super resolution with multiple frames.} To resolve the blurriness of input images, a SR algorithm on a smartphone is required to recover the captured contents. However, none of existing SR algorithms can be adapted for this attack scenario, especially with massive extremely blurred photos as input. Since smartphones can capture 10 snapshots per second in burst mode. Specifically, the difference between videos and multiple snapshots rules out existing image/video super resolution algorithms\cl{citation?}. The reason has two folds. First, either increased input leads to increases in model complexity, making it unsuitable for mobile deployment. Second, the nature of our task requires to do pixel-wise correlation and comparison with same coordinates on consecutive images throughout our construction process. Otherwise we cannot tell if, for example, it is one stroke or two parallel strokes that is shown in these two darker pixels on this photo.
  \item \textbf{Model complexity and variable input.} We have to operate our threat model locally on comercial smartphones in a real-time manner rather than remotely in cloud server. Since 1) the latter would require stable Internet access, and 2) sending multiple images across the Internet will consume time and bandwith. Given the required 10 to 20 images to process for ideal contennt recovery, we have 1-2s as the minimum interval between each output frame, rendering limited period for calculation with restricted power and RAM. In cases where the display on the target screen changes more frequently, less images and processing time are avaliable for each scene. Consequently, it cannot only require a smaller and simpler network model, but also a model that can deal with dyanmic inputs efficiently, either 3 or 20 images.
  \item \textbf{Complexities of characters.} To make our threat model more applicable for real-life scenarios (e.g., passwords or e-mails), we aim for reconstructing multi-type texts, including Chinese characters, English letters, and numbers. And it poses unique challenges compared with scene or object reconstruction. Composed of multiple strokes, characters are distributed discretely in image space, not known to other entities, e.g. faces and natural objects. In some cases, messing up a stroke will not impact its readability, and in other cases shortening or lengthening a stroke even slightly will lead to a different character, leading to misunderstandings. And unlike most SR applications working on similarity (between their output and the ‘ground truth’), our goal is readability, and the network architecture and training process must be engineered accordingly.\cl{ Another challenge is imbalanced data. Among Chinese characters certain strokes and stroke groups are always more commonplace than others, and this imbalanceness often results in lower prediction accuracy over the less common,  unconventionality shaped characters. On the other hand, however, the focus on characters can also aid us. As our network is only expected to reconstructe these characters, the network can learn to detect features from the input and reconstruct strokes and segments from them, extracting more information from the blurry images.}
\end{itemize}

### 2020-06-28 threat_model.tex
abs+parial intro

\section{Threat Model}
\label{sec-threat-model} 
The objective of the attacker is to acquire the information on the smartphone screen of the victim, reading the numbers and English/Chinese characters on screen, with the help of his smartphone’s camera equipped with the SR network we designed. To reduce suspicion, the attacker will probably position himself at about 1.5 meters from the target screen, at an angle within 30 degrees. At this distance few people will be on guard of strangers even when viewing sensitive data or entering passwords. The attacker may raise his phone (one of the latest models with powerful lenses and computational abilities), pretending to be interacting with it, while pointing his camera at the victim. He will extend his zooming ability to the maximum, try to get a focus on the screen (which is difficult to achieve), and take 20 to 30 images in burst mode, with about 0.05 ~ 0.1 seconds of interval between frames. This process will take about 2 seconds, and we assume the information on the screen will not change in this period, nor the position of the screen. These images will be fed to a multi-frame SR network and the result, one single image with higher resolution, will be displayed on the screen soon afterwards. The characters in the image will be reconstructed to the best of the network’s ability, and if successful, the attacker will be able to decipher the information. The above procedure can be automated by an app and repeated every few seconds, giving the attacker a continuous surveillance over the victim’s screen.

>>>>

\section{Threat Model}
\label{sec-threat-model} 
Given the smartphone’s camera equipped with the SR network, the objective of the attacker is to acquire the multi-type of contents accurately on the smartphone screen of the victim from a long range, covering numbers, English and Chinese characters on screen. To reduce suspicion, the attacker will probably position himself at about 1.5 meters from the target screen, at an angle within 30 degrees. Since few people can be on guard of strangers at this distance even when viewing sensitive data or entering passwords. The attacker may raise his phone (one of the latest models with powerful lenses and computational abilities), pretending to be interacting with it, while pointing his camera at the victim. He will extend his zooming ability to the maximum, try to get a focus on the screen (which is difficult to achieve), and take 20 to 30 images in burst mode, with about 0.05 ~ 0.1 seconds of interval between frames. This process will take about 2 seconds, and we assume the information on the screen will not change in this period, nor the position of the screen. These images will be fed to a multi-frame SR network and the result, one single image with higher resolution, will be displayed on the screen soon afterwards. The characters in the image will be reconstructed to the best of the network’s ability, and if successful, the attacker will be able to decipher the information. The above procedure can be automated by an app and repeated every few seconds, giving the attacker a continuous surveillance over the victim’s screen.
